---
title: "Google Play Store"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: 
      version: 4
      bootswatch: cyborg
---


```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(plotly)
library(forcats)
library(tidyverse)
library(RColorBrewer)
data = read.csv("D:/Google playstore Project/dataset/Google-Playstore.csv")
Ratingbins<-data$Rating
cut(Ratingbins,4,labels = c("1-2","2-3","3-4","4-5"))
data$Ratingbins<-cut(Ratingbins,4,labels = c("1-2","2-3","3-4","4-5"))

cols<- c(True="#1f4263", False="#4a99d6")

```



Focus
=====================================

Column {data-width=200}{.tabset .tabset-fade}
-----------------------------------------------------------------------

### Content Rating
```{r}
 #Content Rating
ggplot(mutate(data, Content.Rating = fct_infreq(Content.Rating))) + 
    geom_bar(aes(x = Content.Rating, fill = ..count..))+
  theme(panel.background = element_rect(fill = 'lightblue'))
```

### Pie Chart 

```{r}

freq<-table(data$Content)
fr<-as.data.frame(freq)
fr <- fr %>%
  arrange(desc(Freq))
colo<-c("steelblue4", "steelblue", "steelblue3", "steelblue2", "steelblue1", "skyblue1") 
op <- par(cex = 0.5)
pielabels <- sprintf("%s = %3.1f%s", fr$Var1,
                     100*fr$Freq/sum(fr$Freq), "%")
pie(fr$Freq,
    labels=NA,
    clockwise=TRUE,
    border="black",
    radius=1,
    main ="Percentage of Content of Apps",
    cex.main=2.5,
    col.main="Blue",
    col=colo
)
legend("topleft",legend=pielabels,bty="n", cex=1.3,fill=colo)

```



Column {data-width=600}
-----------------------------------------------------------------------

### Chart Category

```{r}
#Category
library(forcats)
library(tidyverse)

ggplot(mutate(data, Category = fct_infreq(Category))) + 
  geom_bar(aes(x = Category, fill = ..count..)) +
  coord_flip()+
  theme(panel.background = element_rect(fill = 'lightblue'))
```


Column {data-width=200}
-----------------------------------------------------------------------

### Number of Apps

```{r}
valueBox(nrow(data))
```


### Education

```{r}
education = nrow(data[data$Category == "Education",])
valueBox(education)
```


### Music & Audio

```{r}
Music = nrow(data[data$Category == "Music & Audio",])
valueBox(Music)
```


### Tools

```{r}
Tools = nrow(data[data$Category == "Tools",])
valueBox(Tools)
```


### Apps rated Everyone

```{r}
Everyone = nrow(data[data$Content.Rating == "Everyone",])
valueBox(Everyone)
```

Category
=====================================
Column {data-width=900, .tabset .tabset-fade}
-----------------------------------------------------------------------

### Count
```{r}
library(forcats)
library(tidyverse)

ggplot(mutate(data, Category = fct_infreq(Category))) + 
  geom_bar(aes(x = Category, fill = ..count..)) +
  coord_flip()+
  theme(panel.background = element_rect(fill = 'lightblue'))
```


### Ad Supported
```{r}
ggplot(data = data, aes(y=Category, fill= Ad.Supported)) +
  geom_bar() +
  theme(panel.background = element_rect(fill = 'lightblue'))+
   scale_fill_manual(values = cols) 
```


### Free
```{r}
ggplot(data = data, aes(y=Category, fill= Free)) + 
  geom_bar() +
  theme(panel.background = element_rect(fill = 'lightblue'))+
  scale_fill_manual(values = cols) 
```

<!-- ### Rating {.tabset .tabset-fade} -->
<!-- ```{r} -->
<!-- ggplot(data = data, aes(x=Rating, fill= Category)) +  -->
<!--   geom_bar() + -->
<!--   theme(panel.background = element_rect(fill = 'lightblue')) -->
<!-- ``` -->

### Editors Choice {.tabset .tabset-fade}
```{r}
ggplot(data = data, aes(y=Category, fill=Editors.Choice))+
  geom_bar()+
  theme(panel.background = element_rect(fill = 'lightblue'))+
  scale_fill_manual(values = cols) 
```



Column {data-width=200}
-----------------------------------------------------------------------


### Category with most Apps

```{r}
valueBox("Education")
```

### Category with most Free Apps

```{r}
valueBox("Education")
```


### Number of Editors Choice Apps

```{r}
choice <- nrow(data[data$Editors.Choice == "True",])
valueBox(choice)
```


### Category with most number of Ads

```{r}
valueBox("Music & Audio")
```






Rating
=====================================
Column {data-width=625, .tabset .tabset-fade}
-----------------------------------------------------------------------

### Rating Count
```{r}
ggplot(data = data, aes(x=Ratingbins, y= Rating.Count)) + 
  geom_bar(stat='identity',fill='#1f4263') +
  theme(panel.background = element_rect(fill = 'lightblue'))
```

<!-- ### Category -->
<!-- ```{r} -->
<!-- ggplot(data = data, aes(x=Rating, fill= Category)) +  -->
<!--   geom_bar() + -->
<!--   theme(panel.background = element_rect(fill = 'lightblue')) -->
<!-- ``` -->

### PMF and CMF {.tabset .tabset-fade}
```{r}
  Log_Installs <- log(data$Minimum.Installs)
 
  rating_prob <- data %>%
    group_by(Ratingbins) %>%
    summarise(Log_Installs = n()) %>% 
    mutate(pmf = Log_Installs/sum(Log_Installs)) %>% #PMF
    mutate(cdf = cumsum(pmf)) #CDF
  

  plot_rating<- ggplot(rating_prob, aes(x=Ratingbins,y=Log_Installs)) +
    geom_point()+xlab("Ratings ")+
    geom_point()+ylab("Installs")+
  theme(panel.background = element_rect(fill = 'lightblue'))
  plot_rating
```


```


### Content Rating {.tabset .tabset-fade}
```{r}
p1<- ggplot(data = data, aes(x=Rating, fill= Content.Rating)) + 
  geom_bar() +
  theme(panel.background = element_rect(fill = 'lightblue'))

ggplotly(p1)
```


Column {data-width=375}
-----------------------------------------------------------------------

### Ad Supported in various Rating-bins

```{r}
ggplot(data = data, aes(x=Ratingbins, fill= Ad.Supported)) + 
  geom_bar(position='dodge') +
  theme(panel.background = element_rect(fill = 'lightblue'))+
  scale_fill_manual(values = cols) 
```


### Average Rating

```{r}

average <- mean(data$Rating,na.rm = TRUE)
valueBox(average)
```




Additional Knowledge
=====================================
Column {data-width=625, .tabset .tabset-fade}
-----------------------------------------------------------------------

### Free
```{r}
 boxplot <-ggplot(data = data)+geom_boxplot(mapping =aes(x = Free, y = Log_Installs, fill = Free,)) + labs(title="Total Installs(log) by the Type of Application")+ 
    ylab("Total Installs")+ xlab("Application Type") +
  theme(panel.background = element_rect(fill = 'lightblue'))+
  scale_fill_manual(values = cols) 
  boxplot
```

### Free vs Count {.tabset .tabset-fade}
```{r}
    ggplot(data = data)+ geom_bar(mapping =aes(x = Free),color = 'black', fill = '#1f4263')+xlab('Free')+ 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
    labs(title= "Number of Free Apps") +
  theme(panel.background = element_rect(fill = 'lightblue'))+
  scale_fill_manual(values = cols) 
```


### Free vs Ad supported{.tabset .tabset-fade}
```{r}
ggplot(data = data, aes(x=Free, fill= Ad.Supported)) + 
  geom_bar() +
  theme(panel.background = element_rect(fill = 'lightblue'))+
  scale_fill_manual(values = cols) 
```


### Histogram Distribution of Price

```{r}
ggplot(data,aes(x=Price))+
  geom_histogram(fill="navyblue",col="black",binwidth = 100)+
  xlab("Price")+
  theme(panel.background = element_rect(fill = 'lightblue'))
```

### Ad supported

```{r}
ggplot(mutate(data, Ad.Supported = fct_infreq(Ad.Supported))) + 
    geom_bar(aes(x = Ad.Supported, fill = ..count..))+
  theme(panel.background = element_rect(fill = 'lightblue'))

```

### Editors Choice

```{r}
ggplot(mutate(data, Editors.Choice = fct_infreq(Editors.Choice))) + 
    geom_bar(aes(x = Editors.Choice, fill = ..count..))+
  theme(panel.background = element_rect(fill = 'lightblue'))
```


Column {data-width=375}
-----------------------------------------------------------------------

### Free Vs Paid

```{r}
ggplot(mutate(data, Free = fct_infreq(Free))) + 
    geom_bar(aes(x = Free, fill = ..count..))+
  theme(panel.background = element_rect(fill = 'lightblue'))
```


### Number of Apps with no Ads

```{r}
WithoutAds = data[data$Ad.Supported == "False",]
valueBox(nrow(WithoutAds))
```

### Number of Apps with Ads

```{r}
WithAds = data[data$Ad.Supported == "True",]
valueBox(nrow(WithAds))
```




